---
title: "ETC5513: Collaborative and Reproducible Practices"
toc: false
format:
  html:
    page-layout: full
---

This unit develops teamwork skills, through instruction on reproducibility and version control to conduct collaborative data analysis. These skills are practised in a team setting with a data analysis project.

## Learning outcomes

1. Develop skills to create reproducible data analyses
2. Understand the operation of version control systems
3. Utilise version control to integrate data analysis efforts of team members
4. Effectively work with a group to construct a collaborative data story

## Teachers

* [**Michael Lydeamore**](https://www.michaellydeamore.com). Chief Examiner. Email: [michael.lydeamore@monash.edu](mailto:michael.lydeamore@monash.edu)
* [**Naveen Kaushik**](https://www.linkedin.com/in/naveen-kaushik/). Email: [naveen.kaushik@monash.edu](mailto:naveen.kaushik@monash.edu)

```{r}
#| label: load_packages
#| include: false
#| message: false
#| warning: false
#| echo: false
#| cache: false
library(tidyverse)
options(knitr.kable.NA = '')
source(here::here("course_info.R"))
week <- as.integer(1 + ((Sys.Date() - as_date(start_semester))/7))
```

## Weekly schedule

* 2 hour workshop, Thursdays 10am-12pm each week
* 1.5 hour tutorial, one of:
  * Tuesday 6pm-7.30pm
  * Wednesday 4pm-5.30pm
  * Wednesday 5.30pm-7pm

## Consultation

* Michael Lydeamore: Thursday 3pm-4pm hybrid
* David Wu: Tuesday 4-5pm in-person (See Moodle for details)
* Naveen Kaushik: Monday 5.30-7pm online

```{r}
#| label: schedule2
#| message: false
#| warning: false
#| echo: false
#| output: asis
schedule |>
  transmute(
    Date = format(Date, "%d %b"),
    Show = (!is.na(Week) & Week <= 12) & !grepl("University Holiday", Topic),
    Show_Tutorial = !is.na(Week) & Week <= 12,
    Topic = if_else(!Show, Topic, glue::glue('[{{Topic}}](./week{{Week}}/index.html){target="_blank"}', .open="{{", .close="}}")),
    Tutorial = if_else(!Show_Tutorial, "", glue::glue('[{{< fa list-check >}}](./week{{{Week}}}/tutorial/index.html){target="_blank"}', .open="{{{", .close="}}}")),
    Workshop = if_else(!Show, Workshop, glue::glue('[{{< fa list-check >}}](./week{{{Week}}}/workshop/index.html){target="_blank"}', .open="{{{", .close="}}}")),
    Assessments = if_else(is.na(Assignment), Assignment, glue::glue("[{Assignment}]({File})"))
  ) |>
  select(-Show, -Show_Tutorial) |>
  knitr::kable(format = "markdown")
```