---
title: 'ETC5513: Collaborative and Reproducible Practices'
subtitle: "Workshop 2"
author: "Michael Lydeamore"
date: today
format:
    unilur-html: 
        embed-resources: true
        output-file: "index.html"
---

```{r, echo = FALSE, eval = file.exists("tutorial.css")}
htmltools::includeCSS("tutorial.css")
```

::: {.callout-note collapse="true"}
## Preparation

1.  To complete this tutorial, you'll need the pre-built RStudio project. Go to Moodle, under Week 2, download the Tutorial 2 RStudio Project zip.\
    Save this file on your computer and unzip it. You can open the `.Rproj` file and that should launch RStudio.
2.  To render into a PDF, you will need to install the `tinytex` package. There are two methods to do this:\
    Either `install.packages("tinytex")` or at your command line type `quarto install tinytex`. Your tutors can help with this if you get stuck.
:::

## Exercise 1: RStudio Projects

1.  Render the `Tutorial2.qmd` file into a HTML and a PDF.
2.  Write your name as an author in the YAML.
3.  Change the HTML theme to `cerulean`.

::: unilur-solution
Your YAML block should now look something like this:

``` yaml
title: "ETC5513: Tutorial 2 solution"
author: "Michael Lydeamore"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
```
:::

## Exercise 2: YAML and R Chunk Options

Carefully inspect the YAML and the first R code chunk in your Quarto file.

1.  What is the first R chunk of code doing?\
    Hint: Remember all the libraries used in an analysis should be listed together at the top of the file.
2.  Change the R chunk option from `message: false` to `message: true` and add the option `warning: true`. What happens when you knit the file?
3.  Create a new section called Introduction and type using markdown the following:\
    "In this tutorial we are looking at the *Coronavirus* cases detected within the Hubei area as reported in the Lancet Journal website as of March 12, 2019."\
    Hint: Think about the `#` character.
4.  Remove all the R chunk messages from the Chunk called `Chunk 1` and write the following under that section using markdown:\
    "In this section we are loading all the required libraries for the tutorial"
5.  For the same R Chunk, add the chunk option `echo: false`. What does this do?
6.  Using markdown, link the word "Lancet" to the website https://www.thelancet.com/coronavirus

::: unilur-solution
1.  The first R chunk is loading all the libraries we will need for the analysis.
2.  Chunk options in Quarto are specified using the hashpipe, `#|`. Setting `message: true` and `warning: true` provides messages about packages being successfully loaded, and potentially having mismatched versions.

For the remainder of the questions, your markdown should look like this:

```` verbatim
# Introduction

In this tutorial we are looking at the *Coronavirus* cases detected within the Hubei area as reported in the [Lancet](https://www.thelancet.com/coronavirus) Journal website as of March 12, 2019.

```{{r Chunk 1}}
#| message: false
#| warning: false
#| echo: false
#| eval: true
library(rmarkdown)
library(knitr)
library(tidyverse)
library(readr)
library(kableExtra)
library(ggplot2)
library(lubridate)
library(gridExtra)
```
In this section we are loading all the required libraries for the tutorial.
````
:::

```{r}
#| echo: false
#| message: false
#| warning: false

library(rmarkdown)
library(knitr)
library(tidyverse)
library(readr)
library(kableExtra)
library(ggplot2)
library(lubridate)
library(gridExtra)

dat <- read_csv("Data/COVID19_March12_Hubei.csv")
```